TBD

### 2016-08-31 paper/paper.tex
+ CEGIS figure

@@

\section{Introduction}
\section{Overview}
\section{Running Example}
\section{Program Synthesis}
\section{Experiments}
\section{Related Works}
\section{Conclusions}

>>>>

\usepackage{url}                  % format URLs
\usepackage{listings}          % format code
\lstset{
  mathescape, 
  language={Java},
  basicstyle=\small
}
\usepackage{enumitem}      % adjust spacing in enums
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   
\usepackage{graphicx}
\usepackage{float,subfig}
\usepackage{xspace,framed}
\usepackage{colortbl}
\usepackage{calc}

\usepackage{algorithm}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
\usepackage[justification=centering]{caption}
\usepackage{stmaryrd}
\usepackage{hhline}
\usepackage{pifont}
%\usepackage{cite}
\usepackage{pdflscape} % Experiments table is landscape
\usepackage{longtable}
\usepackage{afterpage}
\usepackage{wasysym}

@@

\section{Introduction}
\section{Overview}
\section{Running Example}
\section{Program Synthesis}

We use CounterExample-Guided Inductive Synthesis (CEGIS), as illustrated in Fig~\ref{fig:CEGIS}.

\begin{figure*}
\centering
\resizebox{.6\textwidth}{!}{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto,
 semithick, initial text=, ampersand replacement=\&,]

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=1cm] {
   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}}; \\
   \node[fill=yellow!20] (synth) {{\sc Synthesise}};
   \&
   \node[fill=yellow!20] (verif) {{\sc Verify}}; \\
   %% \&

   \& \\
   \& \\
   \node (gp) {~~~~~~~~~~~~~~Program Search~~~~~~~~~~~~~~~};
   \&
   \node (bmc) {~~~~~~~~~~~~~~~BMC-based Verifier~~~~~~~~~~~~~~~};

    \\
  };

   \path
    ([yshift=2em]synth.east) edge node {Candidate solution} ([yshift=2em]verif.west)
    ([yshift=-2em]verif.west) edge node {Counter-ex} ([yshift=-2em]synth.east)
    ([xshift=5em]verif.south) edge node {Candidate $P$} ([xshift=5em]bmc.north)
    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif.south)
    (verif) edge node {} (done)
    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south);
 \end{tikzpicture}
}
 \caption{Counterexample-Guided Inductive Synthesis. \label{fig:CEGIS}}
\end{figure*}

\section{Experiments}
\section{Related Works}
\section{Conclusions}
